Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-01 Geometric types.tex

\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n\circ s = \id_G},

@@

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $q\ab^*: \CS(G\ab) \to \CSab(G)$.
\end{proposition}
\begin{proof}
%To simplify notation below, set $H=G\der$.
Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, it is also an $G\der$-torsor in the fpqc topology.

It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 
For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
%
Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.
Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.

>>>>

\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n=p\circ s = \id_G},

@@

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $q\ab^*: \CS(G\ab) \to \CSab(G)$.
\end{proposition}
\begin{proof}
It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 
For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
%
Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.
Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.
